Checklist

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] WIP shutdown list

\makeatletter
\newcommand\ColorBox[2]{
  \begin{tikzpicture}
    \fill[#1] (0, 0) rectangle (\f@size/25, \f@size/25);
    \path (\f@size/50, \f@size/50) node[color=black!15] {\small #2};
  \end{tikzpicture}
}
\newcommand\DevBoxes{{\Large\ColorBox{color=red!50}{Off}\!\!\ColorBox{color=green!50}{On}}}
\newcommand\OffBox{{\normalsize\ColorBox{color=orange!50}{}}}
\newcommand\OnBox{{\normalsize\ColorBox{color=cyan!50}{}}}
\makeatother

@@

  \begin{tabular}{|c|c|}
    \hline
    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
    Left Current&\\\hline
    Right Voltage&\\\hline
    Right Current&\\\hline
  \end{tabular}\\
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
\item\DevHeader{1st version Till's current controller for Cs MOT}
  Record current value:\\
  \begin{tabular}{|c|c|}
    \hline
    Current&\hphantom{\hspace{3.5cm}}\\\hline
  \end{tabular}\\
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \item\OnBox Plug in power
  \item\OnBox Turn on
\item\DevHeader{Homebuilt $\pm15,5$V power supply}
  \textbf{2nd level above Cs tweezer/MOT lasers}\\
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \item\OnBox Plug the load back in

>>>>

\makeatletter
\newcommand\ColorBox[2]{
  \begin{tikzpicture}
    \fill[#1] (0, 0) rectangle (\f@size/25, \f@size/25);
    \path (\f@size/50, \f@size/50) node[color=black!15] {\small #2};
  \end{tikzpicture}
}
\newcommand\DevBoxes{\mbox{{\Large\ColorBox{color=red!50}{Off}\!\!\ColorBox{color=green!50}{On}}}}
\newcommand\OffBox{{\normalsize\ColorBox{color=orange!50}{}}}
\newcommand\OnBox{{\normalsize\ColorBox{color=cyan!50}{}}}
\makeatother

@@

  \begin{tabular}{|c|c|}
    \hline
    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
    Left Current&\\\hline
    Right Voltage&\\\hline
    Right Current&\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
\item\DevHeader{1st version Till's current controller for Cs MOT}
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Record current value:\\

  \begin{tabular}{|c|c|}
    \hline
    Current&\hphantom{\hspace{3.5cm}}\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
\item\DevHeader{Homebuilt $\pm15,5$V power supply}
  \textbf{2nd level above Cs tweezer/MOT lasers}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
\item\DevHeader{Cs 1.0 MOT lock box}
  \textbf{1st level above Cs MOT lasers}
  \begin{itemize}
  \item\OffBox Make sure the laser is unlocked.
  \end{itemize}
\item\DevHeader{Novatech function generator}
  \textbf{1st level above Cs MOT lasers}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Save settings
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Restore settings
  \end{itemize}\vspace{1cm}
\item\DevHeader{New Focus Cs Raman lasers drivers (2x)}
  \textbf{1st level above Cs Raman lasers}\\
  Record Temperature, Current, Piezo voltage\\
  Temperature is accessible in the menu under system status\\

  \begin{tabular}{|c|c|}
    \hline
    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
    F3 Piezo Voltage&\\\hline
    F3 Temperature&\\\hline
    F4 Current&\\\hline
    F4 Piezo Voltage&\\\hline
    F4 Temperature&\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox (Turn on)
  \end{itemize}
\item\DevHeader{Benchtop power supply}
  \textbf{1st level next to Cs Raman driver}\\
  Record voltage/current values:\\

  \begin{tabular}{|c|c|}
    \hline
    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
    Current&\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
\item\DevHeader{Homebuilt $24$V power supply}
  \textbf{2nd level above Cs Raman lasers}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
\item\DevHeader{SRS shutter driver}
  \textbf{1st level above Cs Raman lasers}\\
  Switch off/on with the switch on the back.
\item\DevHeader{New Focus lock box for Cs Raman}
  \textbf{1st level above Cs Raman lasers}\\
  Unplug power.
\item\DevHeader{Timebase driver for Na Raman and Na D2 (x2)}
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record current and T1 settings\\

  \begin{tabular}{|c|c|}
    \hline
    Raman Current&\hphantom{\hspace{3.5cm}}\\\hline
    Raman T1&\\\hline
    MOT Current&\hphantom{\hspace{3.5cm}}\\\hline
    MOT T1&\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \item\OnBox Set current/temperature.
  \item\OnBox Enable T1 survo
  \item\OnBox Turn on current
  \end{itemize}
\item\DevHeader{Thorlabs temperature controller for Na Raman doubler}
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record temperature settings\\

  \begin{tabular}{|c|c|}
    \hline
    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check temperature setting
  \item\OnBox Turn on
  \end{itemize}
\end{itemize}
